---
title: "ST558 HW1"
author: "Kyra Kapsaskis"
format: html
editor: visual
---

## My first homework

## Data Science

answer the questions here What do you think being a data scientist is about? ∗ What differences/similarities do you see between data scientists and statisticians? ∗ How do you view yourself in relation to these two areas?

## first bit of code

```{r}
y <- density(iris$Sepal.Length)
```

-   Create an R code chunk to determine the class, type, and structure of the object y
-   Create an R code chunk that uses the plot function on y. Hide the R code in the final document by setting echo to false.
-   Include some markdown test between these code chunks explaining what you are doing with the R code.

# finding the class

```{r}
class(y)
```

# finding the type

```{r}
typeof(y)
```

# finding the structure

```{r}
str(y)
```

# plotting the y variable

```{r,echo=FALSE}
plot(y, main = "Density Plot of Sepal Length")
```
## created connection between my github and R Studio and pushed my commits. 